%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% CV Jakša Tomović 06/2019 %%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[10pt,a4paper]{altacv}

%Layout
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm,footskip=2\baselineskip}

%Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage{hyperref}
%\usepackage{academicons}

%Colors

\definecolor{accent}{HTML}{000e17}
\definecolor{heading}{HTML}{000e17}
\definecolor{emphasis}{HTML}{696969}
\definecolor{body}{HTML}{01415f}

\colorlet{heading}{heading}
\colorlet{accent}{accent}
\colorlet{emphasis}{emphasis}
\colorlet{body}{body}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle


%   
}


%

\begin{document}
\name{Joao Tiago Aparicio}
\tagline{}
%\photo{2.5cm}{BrunoAlves}
\personalinfo{
    \email{joaotiagoaparicio@gmail.com}
    \homepage{jtaca.github.io/}
    \github{jtaca}
    \linkedin{linkedin.com/in/jtaca}
}

%

\begin{fullwidth}
\makecvheader
\end{fullwidth}

%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection[page1sidebar]{Experience}

%%%%%%%%%%%%%
%Experience 1
%%%%%%%%%%%%%

\cvevent{Undergraduate Research Assistant}{Instituto de Telecomunicacoes \quad ( \url{https://it.pt/})}{Nov. 2018 - Apr. 2019}{Lisbon, Portugal}
\begin{itemize}
    \setlength{\itemindent}{0.5em}
    \item[--]   \small{Worked on web scrapping and text extraction algorithms}
\end{itemize}

\medskip

%%%%%%%%%%%%%
%Experience 2
%%%%%%%%%%%%%

\cvevent{Chair}{ACM Student Chapter at ISCTE-IUL}{Dec. 2016 - Feb. 2019}{Lisbon, Portugal}

%\begin{itemize}
%    \item Fullstack JAVA developer
%\end{itemize}

\begin{itemize}
    \setlength{\itemindent}{0.5em}
    \item[--]   \small{Organized events, managed teams and participated in coding competitions}
    \item[--]  \small{Gave 5 different talks in Robotics }
     \item[--]  \small{Participated in \textcolor{orange}{Google Hash Code} 2 times}
\end{itemize}
\medskip
\cvevent{Chair of the Robotics and Automation Society}{IEEE Student Branch ISCTE-IUL }{Oct. 2016 - Jul. 2019}{Lisbon, Portugal}

\begin{itemize}
    \setlength{\itemindent}{0.5em}
    \item[--]   \small{Built robots for 2 competitions and managed 2 teams}
\end{itemize}
\medskip

\cvevent{Mentor}{CoderDojo-LX}{Apr. 2015 - Oct. 2017}{Lisbon, Portugal}

\begin{itemize}
    \setlength{\itemindent}{0.5em}
    \item[--]   \small{Teaching the fundamentals of programming and electronics for project-based learning.}
\end{itemize}
\medskip





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection[page2sidebar]{Projects}


\cvevent{}{A retrieval-based Chatbot}{October 2019}{Lisbon Portugal}

\begin{itemize}
  \setlength{\itemindent}{0.5em}
    \item[--]   \small{Based on an original algorithm with similarity metrics.}
\end{itemize}

\cvevent{}{Laboratory Crop Monitoring}{March 2019 -- May 2019}{Lisbon Portugal}

\begin{itemize}
  \setlength{\itemindent}{0.5em}
    \item[--]   \small{Monitoring software for greenhouse with sensors, using distributed databases.}
\end{itemize}

\cvevent{}{Bom Dia Academia}{October 2018 -- December 2018}{Lisbon Portugal}

\begin{itemize}
  \setlength{\itemindent}{0.5em}
    \item[--]   \small{Content aggregation platform for the ISCTE-IUL community. }
\end{itemize}



%%%%%%%%%%%%%
%Project 1
%%%%%%%%%%%%%

\cvevent{}{National and International Robotics Competitions}{Apr. 2012 - Apr. 2017}{Portugal; Mexico; Brazil;}

\begin{itemize}
\setlength{\itemindent}{0.5em}
  \item[--]   \small{Participated in Robocup Junior Rescue and Robot@Factory, Robo Bombeiro (Firefighting Robot) and  Robotop}
\end{itemize}

\divider

%

%%%%%%%%%%%%%
%Project 2
%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Certificates %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Honors \& Awards}

%%%%%%%%%%%%%
%Certificate 1
%%%%%%%%%%%%%
\begin{itemize}
\setlength{\itemindent}{0.5em}
    \item[--]   \small{2016-2018: ISTA TOP Talent Award \textcolor{orange}{(Academic merit award)}}
    \item[--]   \small{2017: ISCTE-IUL Research Week Finalist}
     \item[--]   \small{2016: 4th Place, National Robotics Competition: Robocup Rescue Maze (Portugal)}
    \item[--]   \small{2014: 2nd Place, FCUL Rally Pro \textcolor{orange}{(Programming Competition)}}
    \item[--]   \small{2012-2014: 3rd Place, National Robotics Competition: Robocup Rescue (Portugal)}
  \item[--]   \small{2012: Best Presentation Award: Worldwide Robotics Competition: Robocup Junior 2012}
\end{itemize}
  




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Interests %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \cvsection{Interests}

% \wheelchart{1.5cm}{0.5cm}{%
%   10/10em/accent!30/Electronics,
%   25/9em/accent!60/Science,
%   5/13em/accent!10/Movies,
%   20/15em/accent!40/Sport,
%   30/9em/accent/Technology,
%   5/8em/accent!20/Literature
% }


%%New Page
% \clearpage




\end{document}
